### 2021-08-23 README.Rmd
Text names for SAU now work in all current plots and tables. No EWN.

@@

* 2021-08-13   aMSE 0.0.0.500 removed NumNe (midyear numbers-at-size) and introduced cutcatchN as an argument to do_MSE, which removes all size class data from teh catchN array with size-classes less than cutcatchN, whose default = 56 (2 - 110mm removed). This saves a good deal of space.

>>>>

* 2021-08-23 aMSE 0.0.0.300 Using text as SAU names in the control file now labels all plots and those labels are not included in the tables. glb$saunames now contains the text labels. Other changes include generalizing the number of plots to match number of SAU in all cases (I hope), There is also, now, a ConstantCatchHS.R file in the data-raw sub-directory that allows for a constant catch to be applied to each SAU. This demonstrates that the issue when using the TasmanianHS.R file is not the aMSE package but how the Tasmanian HS functions work with the available data.

@@
